### 2017-12-23 Paper/bg.tex
working on background

In this work, we construct sparse PCEs with LAR using UQLab~\cite{Marelli:2014},
a general purpose Uncertainty Quantification software developed at ETH Zurich in Switzerland.

>>>>

The regularization term forces the minimization towards low-rank solutions.
In this work, we construct sparse PCEs with LAR using UQLab~\cite{Marelli:2014},
a general purpose uncertainty quantification software developed at ETH Zurich in Switzerland.
